### 2011-11-01 paper.tex
edits

Introducing the placeholder $\gamma$ as an additional terminal, define
\begin{eqnarray*}
\m(i,j,k,l,A) & = & \seqweight{((\gamma)A)\epsilon}{\outsubseq{i}{j} \gamma \outsubseq{k}{l}} \\
\mtip(i,l,A) & = & \seqweight{((\epsilon)A)\epsilon}{\outsubseq{i}{l}}
\end{eqnarray*}
where $1 \leq i \leq j \leq k \leq l \leq |\outseq|$.

@@

@@

The DP recursion relation is as follows (with $B,C,V,X,u,v,x,y$ defined as in \tabref{RuleTypes})
\begin{eqnarray*}
\lefteqn{\m(i,j,k,l,A) =} \\
& &
\sum_{\rho \in \rulesubset{BIF}{A}} \sum_{m=i}^j W(\rho) \mtip(i,j,V) \mtip(k,l,X) \\
& & +
\sum_{\rho \in \rulesubset{ADJ}{A}} \sum_{m=i}^j \sum_{n=k}^l W(\rho) \m(i,m,n,l,B) \m(m,j,k,n,C) \\
& & +
\sum_{\rho \in \rulesubset{EMT}{A}} W(\rho) \m(i+|u|,j-|v|,k+|x|,l-|y|,C) \iumatch \jvmatch \kxmatch \lymatch
\end{eqnarray*}

>>>>

Dynamic programming is breaking down a problem recursively into a lot of smaller problems,
whose solutions can be tabulated and re-used in computing the bigger problem.
Here, the big problem is to find the probability (weight) that the initial symbol $\startsymbol$ will derive the output sequence $\outseq$.
The smaller problems are the probabilities that a given symbol $A$ will derive sequences $\outsubseq{i}{j}$ to the left and $\outsubseq{k}{l}$ to the right.

Introducing the additional terminal $\gamma$ as a placeholder for the sequence $\outsubseq{j}{k}$, define
\begin{eqnarray*}
\m(i,j,k,l,A) & = & \seqweight{((\gamma)A)\epsilon}{\outsubseq{i}{j} \gamma \outsubseq{k}{l}} \\
\mtip(i,l,A) & = & \seqweight{((\epsilon)A)\epsilon}{\outsubseq{i}{l}}
\end{eqnarray*}
where $1 \leq i \leq j \leq k \leq l \leq |\outseq|$.

@@

The final derivation weight is
\[
\seqweight{\startsymbol}{\outseq} = \mtip(1,|\outseq|,\startsymbol)
\]

@@

The DP recursion relation is as follows (with $B,C,V,X,u,v,x,y$ defined as in \tabref{RuleTypes})
\begin{eqnarray*}
\lefteqn{\m(i,j,k,l,A) =} \\
& &
\sum_{\rho \in \rulesubset{BIF}{A}} W(\rho) \mtip(i,j,V) \mtip(k,l,X) \\
& & +
\sum_{\rho \in \rulesubset{ADJ}{A}} \sum_{m=i}^j \sum_{n=k}^l W(\rho) \m(i,m,n,l,B) \m(m,j,k,n,C) \\
& & +
\sum_{\rho \in \rulesubset{EMT}{A}} W(\rho) \m(i+|u|,j-|v|,k+|x|,l-|y|,C) \iumatch \jvmatch \kxmatch \lymatch
\end{eqnarray*}
